Can Auxiliary Indicators Improve COVID-19 Forecasting and Hotspot Prediction?

### 2021-09-30 forecast/paper/response-to-reviewers.tex

\begin{resp}
  We thank the editor and reviewers for their comments and the opportunity to make
  revisions. We have made a number of revisions, described in detail below.
  We believe these changes have strengthened the manuscript, and describe them in
  more detail below.
  We quote below the Reviewer comment and provide our response in this color.
\end{resp}

\section*{Reviewer 1}

  1. In their presentation of of evaluation metrics they do not discuss
  stability. For instance in [7] does the choice of the weights, using $\tau$ for
  $x\geq 0$ rather than some monotone function say some power $\tau^\alpha$ make a
  difference? Since as they indicate the measure is used for fitting as well as
  ascertainment, some stability investigation seems appropriate. I suspect here
  is no great effect but...

\begin{resp}
  The reviewer is correct: the choice of $\tau$ rather than a monotone function of
  $\tau$ will make a difference. But it seems that we should have been more clear
  in our description of WIS. The weights used here are those used to evaluate
  forecasts submitted to the COVID-19 Forecast Hub and the CDC. More broadly,
  this is a standard metric in the forecasting community (just as Mean Squared
  Forecast Error is standard), rather than an ``author decision''.  With the
  weights as used, it is equivalent to quantile loss and therefore is a discrete
  version of CRPS (see [7]).

  In principle,
  we would expect that different weights may alter the conclusions, though
  likely not substantively. Applying a monotone function to $\tau$ only effectively
  changes the quantile of interest, resulting in a mismatch between the coverage you
  tried to get and the coverage WIS is evaluating. Applying the function to $\tau$
  and $(1-\tau)$ results in an asymmetry, penalizing forecasts that miss on one
  side more than on the other.

@@

\section*{Reviewer 2}
\begin{quote}
  \emph{(items numbered by the editor for convenience of reference)}
\end{quote}

\subsection*{Statistical or Methodological Comments:}

1. Is this really a stationary phenomenon? Over the timerange extending from
pre-lockdown to today, it certainly isn't. The method in this paper of
presenting model prediction errors makes it impossible to see this. People in
econometrics look at cumsums of normalized prediction errors. You can see change
points and trends very easily.

\begin{resp}
  There is little reason to believe that this data is stationary. The models
  however are trained and evaluated over reasonably short periods (2-3 months),
  over which time the behavior may well be stationary. We have added a section
  to the appendix that uses the cumulative sum normalized by baseline as
  suggested. With some exceptions at the beginning of 
  the evaluation period, the relative ordering remains fairly consistent. The AR
  model is easily the worst.

@@

\end{resp}

2. Are the results in this paper statistically significant? I see no discussion
of this question, which seems unbelievable for me to be saying, given the
authorship. And yet here I am.

\begin{resp}
  This is an important point that we should have addressed more fully.
  Conventional methods for assessing statistical significance that we explored
  were overconfident, to the point of being unbelievable due to the
  spatiotemporal correlation.

@@

  We also have strong reasons for not using model-based approaches (one being the
  nonstationarity the Reviewer mentions above, but also the belief that these
  models are wrong). We felt that the related investigation in 2B was more
  pertinent.

  To respond more directly we have made a number of additions.:

  $\bullet$ We have added a section to the Supplement (and point
  to it around 
  line 85 in the main text), that performs a Sign Test for differences in
  accuracy. P-values there tend to cluster near zero and one suggesting some
  periods have significantly improved accuracy for the indicator-assisted models
  while in others, the reverse is true.

  $\bullet$ We also use a Diebold-Mariano test
  for comparing forecast accuracy. The results for this test are mixed, as would
  be expected given the sign test and
  the nonstationarity the Reviewer mentions above. The indicators are
  more helpful in some periods than others, see also the upswing/downswing
  discussion in Section 2C. 
\end{resp}

@@

3. Are the results in this paper practically significant? I see no discussion of
this question, which seems unbelievable for me to be saying, given that the
authors refuse to consider statistical significance. And yet here I am.

\begin{resp}
  See also Reviewer 1 point 3. And the general comment below (Point 8) where we
  outline some specific changes we have made that bare on this point.

  Practically, on average, if our goal is to predict 11 days ahead, when the AR
  model is at its best, CHNG-CLI
  doesn’t help (at least with these simple models). However, CHNG-COVID,
  DV-CLI, and Google-AA ``buy'' 4 extra days for the 
  same accuracy. CTIS-CLIIC ``buys'' about 5 extra days. What we mean here is
  that if we have a certain tolerance for inaccuracy, adding these signals increases the
  horizon at which we can predict within our tolerance. As for the
  practical significance of 4-5 extra days, this would of course depend on the use case.  However, cases grow
  exponentially, so making public policy changes 15 or 16 days ahead rather than
  11 can mean real gains. There also seems to be a fairly constant mapping
  between cases and future hospitalizations. Giving
  hospitals a few extra days to accumulate supplies and find personnel is
  meaningful. For predicting hotspots, we see similar results (gains of a few
  days) though with different indicators. 
\end{resp}

@@

\begin{resp}
  We have tried to focus mainly on simple time series models in this paper
  rather than comparing to other more elaborate models. A careful
  (out-of-sample) comparison of forecasting performance for state-of-the-art
  models can be found in reference 6 (Cramer et al.). That paper focuses on
  forecasting deaths rather than cases and at the state-level rather than
  disaggregated HRRs. However, their ranking (Figure 2 of Cramer et al.) puts the
  ``COVIDhub-Baseline'' about 10th out of 27 models. As we discuss in the
  manuscript, that baseline is  
  the
  same as the baseline we use for forecasting in this paper: it propagates today
  forward and resamples the residuals to create quantiles (we have expanded the
  description on page 6 to be more explicit). All our ``simplistic'' models beat
  this baseline (the AR(3) does as well). For comparison, IHME (along with 17 other
  ``state-of-the-art'' models) does not. We would argue that using any of the
  models in this paper would be preferable to relying on many of the
  ``widely-used'' models if the goal is forecast accuracy.

  $\bullet$ We have added a sentence to the introduction (around line 40) that
  describes the performance of simple models relative to widely-used models as
  shown in Cramer et al.

  $\bullet$ We have expanded our description of our baseline model (around line
  457). In particular, we emphasize that it is the same as that used by the
  COVID-19 Forecast Hub.

  $\bullet$ We have added two figures to the supplement along with a section of
  text (Section 9) that compares our forecasts with state-of-the-art forecasts
  submitted to the COVID-19 Forecast Hub. The first (Figure S26) overlays the
  scores from the submissions on top of Figure 3 from the manuscript. We should
  note that the submitted forecasts are at the state level, while ours are at
  the HRR level, but once scaled by the baseline, should be roughly comparable.
  Only those forecasters that submitted at least 300 forecasts (roughly 50
  states over 6 weeks during the 6 months examined) are shown. From this Figure
  it is clear that all of the forecasters considered in this paper beat most
  submissions. In the second figure, we use the Geometric Mean scaled by the
  baseline, which should be a more meaningful comparison, as argued elsewhere in
  the supplement. By this metric, the methods employed in this
  paper would rank in the top 2 of all submitted forecasts, beating the
  COVIDhub-ensemble at all forecast 
  horizons. The improvement of the best indicator assisted model over the AR model
  is roughly the same as the improvement of the AR model over the COVIDhub-ensemble.
\end{resp}

### 2021-09-30 forecast/paper/supplement.Rmd

```{r upswing-summary, fig.cap="Average difference between the WIS of the AR model and the WIS of the other forecasters. The indicator-assisted forecasters do best during down and flat periods."}
# Figure 5 in the manuscript
up_down_df_summary <- up_down_df %>%
  filter(period != "jm") %>%
  group_by(forecaster, udf) %>%
  summarise(mean = Mean(AR_wis - wis))
up_down_df_summary %>%
  ggplot(aes(udf, mean , fill = forecaster)) +
  geom_bar(width = 0.6, position = position_dodge(width=0.6),
           stat = "identity") +
  scale_fill_manual(values = fcast_colors[1:5], guide = guide_legend(nrow = 1)) +
  scale_y_continuous() +
  theme_bw() +
  geom_hline(yintercept = 0) +
  ylab("Mean of WIS(AR) - WIS(F)") +
  xlab("") +
  theme(legend.position = "bottom", legend.title = element_blank())
```

@@

@@

```{r cumulative-mean, fig.cap="This figure shows the cumulative sum of WIS for each forecaster divided by the cumulative sum of WIS for the baseline model. The shaded background shows total U.S. cases as reported by JHU-CSSE." }
cumulatives <- fcasts_honest %>%
  group_by(forecaster, forecast_date) %>%
  summarise(mw = Mean(wis),
            smw = Mean(strawman_wis),
            gmw = GeoMean(wis / strawman_wis)) %>%
  arrange(forecast_date) %>%
  mutate(`Cumulative Mean` = cummean(mw) / cummean(smw),
         `Cumulative Sum` = cumsum(mw) / cumsum(smw),
         `Cumulative Geo Mean` = exp(cummean(log(gmw))),
         `GM Regret` = cumsum(gmw) - cumsum(smw/smw),
         `AM Regret` = cumsum(mw) - cumsum(smw),
         `14 day trailing average` = RcppRoll::roll_meanl(mw / smw, n = 14L))

us_cases <- covidcast::covidcast_signal(
  "jhu-csse", "confirmed_7dav_incidence_num", "2020-03-01", "2021-01-01",
  geo_type = "nation") %>% as_tibble() %>%
  mutate(value = (value / max(value)) * .25 +  .75) %>%
  filter(time_value > "2020-06-01")

ggplot(cumulatives %>% filter(forecast_date < "2021-01-01"), 
       aes(forecast_date, color = forecaster)) + 
  geom_line(aes(y = `Cumulative Sum`)) +
  annotate(x = us_cases$time_value, ymax = us_cases$value, ymin = -Inf,
           geom = "ribbon", alpha = .1) +
  geom_hline(yintercept = 1) +
  xlab("forecast date") +
  scale_color_manual(values = fcast_colors, guide = guide_legend(nrow = 1)) +
  theme_bw() +
  theme(legend.position = "bottom", legend.title = element_blank())
```

@@

>>>>

```{r upswing-summary, fig.cap="Average difference between the WIS of the AR model and the WIS of the other forecasters. The indicator-assisted forecasters do best during down and flat periods."}
up_down_df_summary <- up_down_df %>%
  filter(period != "jm") %>%
  group_by(forecaster, udf) %>%
  summarise(mean = Mean(AR_wis - wis))
up_down_df_summary %>%
  ggplot(aes(udf, mean , fill = forecaster)) +
  geom_bar(width = 0.6, position = position_dodge(width=0.6),
           stat = "identity") +
  scale_fill_manual(values = fcast_colors[1:5], guide = guide_legend(nrow = 1)) +
  scale_y_continuous() +
  theme_bw() +
  geom_hline(yintercept = 0) +
  ylab("Mean of WIS(AR) - WIS(F)") +
  xlab("") +
  theme(legend.position = "bottom", legend.title = element_blank())
```

```{r upswing-summary-remake, fig.cap="REMAKE: Percent change in average WIS of the forecaster (AR or indicator assisted) relative to the baseline. All models perform poorly durning down periods, but the indicators help. During flat periods, the indicators improve slightly over the AR. During up periods, all forecasters do much better than the baseline, but only some do as well as AR."}
up_down_df_summary <- inner_join(
  left_join(
    corr_df, 
    fcasts_honest %>% select(ahead, geo_value, forecast_date, strawman_wis)),
  up_down, by = c("geo_value","target_end_date")) %>%
  filter(period != "jm") %>%
  group_by(forecaster, udf) %>%
  summarise(mean = Mean(wis) / Mean(strawman_wis) - 1)
up_down_df_summary %>%
  ggplot(aes(udf, mean, fill = forecaster)) +
  geom_bar(width = 0.6, position = position_dodge(width=0.6),
           stat = "identity") +
  scale_fill_manual(values = fcast_colors, guide = guide_legend(nrow = 1)) +
  theme_bw() +
  scale_y_continuous(labels = scales::percent_format()) +
  geom_hline(yintercept = 0) +
  ylab("% change in Forecaster WIS\n relative to Baseline") +
  xlab("") +
  theme(legend.position = "bottom", legend.title = element_blank())
```

@@

```{r hotspots-upswing-downswing-remake, fig.cap="REMAKE: Classification and loglikelihood separated into periods of upswing, downswing, and flat cases. The indicator assisted models always have lower classification error relative to the null classifier, while the AR actually does worse in down and flat periods. In terms of loglikelihood, all forecasters have lower likelihood than the null classifier during up periods. In down and flat periods, the indicators generally improve over the AR, while the are worse during up periods."}
hot_udf <- inner_join(
  hotspots_honest %>% filter(period != "jm"),
  up_down %>% select(geo_value, target_end_date, udf))

con_tab <- hot_udf %>% 
  filter(!is.na(actual)) %>%
  mutate(pred = value > cutoff) %>%
  group_by(forecaster, udf) %>%
  summarise(m = mean(pred != actual) - .5) %>%
  ungroup()

# con_tab <- left_join(
#   con_tab %>% filter(forecaster != "AR"),
#   con_tab %>% filter(forecaster == "AR") %>%
#     select(-forecaster) %>%
#     rename(mar = m))

llike_tab <- hot_udf %>%
  filter(!is.na(actual)) %>%
  mutate( # kill prob 0-1 predictions
    value = case_when(
      value < 1e-8 ~ 1e-8,
      value > 1-1e-8 ~ 1-1e-8,
      TRUE ~ value
    ),
    llike = (actual == 1) * log(value) + (actual == 0) * log(1 - value),
    nulldev = (actual == 1) * log(.5) + (actual == 0) * log(1 - .5)) %>%
  group_by(forecaster, udf) %>%
  summarise(m = mean(llike) - mean(nulldev)) %>%
  ungroup()

# llike_tab <- left_join(
#   llike_tab %>% filter(forecaster != "AR"),
#   llike_tab %>% filter(forecaster == "AR") %>%
#     select(-forecaster) %>%
#     rename(mar = m))

bind_rows(con_tab %>% mutate(err = "Classification error"), 
          llike_tab %>% mutate(err = "Log likelihood")) %>%
  ggplot(aes(udf, m , fill = forecaster)) +
  geom_bar(width = 0.6, position = position_dodge(width=0.6),
           stat = "identity") +
  scale_fill_manual(values = fcast_colors, guide = guide_legend(nrow = 1)) +
  #scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme_bw() +
  geom_hline(yintercept = 0) +
  facet_wrap(~err, scales = "free_y") +
  ylab("Improvement relative to the null classifier") +
  xlab("") +
  theme(legend.position = "bottom", legend.title = element_blank())
```

@@

```{r cumulative-mean, fig.cap="This figure shows the cumulative sum of WIS for each forecaster divided by the cumulative sum of WIS for the baseline model. The shaded background shows total U.S. cases as reported by JHU-CSSE for the 14-day ahead target. Hashes along the $x$-axis denote weeks." }
cumulatives <- fcasts_honest %>%
  group_by(forecaster, forecast_date) %>%
  summarise(mw = Mean(wis),
            smw = Mean(strawman_wis),
            gmw = GeoMean(wis / strawman_wis)) %>%
  arrange(forecast_date) %>%
  mutate(`Cumulative Mean` = cummean(mw) / cummean(smw),
         `Cumulative Sum` = cumsum(mw) / cumsum(smw),
         `Cumulative Geo Mean` = exp(cummean(log(gmw))),
         `GM Regret` = cumsum(gmw) - cumsum(smw/smw),
         `AM Regret` = cumsum(mw) - cumsum(smw),
         `14 day trailing average` = RcppRoll::roll_meanl(mw / smw, n = 14L))

us_cases <- covidcast::covidcast_signal(
  "jhu-csse", "confirmed_7dav_incidence_num", "2020-03-01", "2021-02-01",
  geo_type = "nation") %>% as_tibble() %>%
  mutate(value = (value / max(value)) * .25 +  .75) %>%
  filter(time_value > "2020-06-01")
ticks <- seq(min(us_cases$time_value), max(us_cases$time_value), by = 7) - 14

ggplot(cumulatives %>% filter(forecast_date < "2021-01-01")) + 
  geom_line(aes(forecast_date, y = `Cumulative Sum`, color = forecaster)) +
  annotate(x = us_cases$time_value - 14, ymax = us_cases$value, ymin = -Inf,
           geom = "ribbon", alpha = .1) +
  annotate("segment", x=ticks, y=-Inf, xend = ticks, yend = .77, 
               color = "grey70") +
  geom_hline(yintercept = 1) +
  xlab("forecast date") +
  coord_cartesian(#ylim = c(.76, 1), 
                  xlim = ymd(c("2020-06-01", "2021-01-01"))) +
  scale_x_date(date_breaks = "2 months", date_minor_breaks = "1 week",
               date_labels = "%b %Y") +
  scale_color_manual(values = fcast_colors, guide = guide_legend(nrow = 1)) +
  theme_bw() +
  theme(legend.position = "bottom", legend.title = element_blank(),
        panel.grid.minor.x = element_blank())
```

```{r cumulative-geo-mean, fig.cap="This figure shows the cumulative geometric mean of WIS for each forecaster divided by the WIS for the baseline model. The shaded background shows total U.S. cases as reported by JHU-CSSE for the 14-day ahead target. Hashes along the $x$-axis denote weeks." }
ggplot(cumulatives %>% filter(forecast_date < "2021-01-01")) + 
  geom_line(aes(forecast_date, y = `Cumulative Geo Mean`, color = forecaster)) +
  annotate(x = us_cases$time_value - 14, ymax = us_cases$value, ymin = -Inf,
           geom = "ribbon", alpha = .1) +
  annotate("segment", x=ticks, y=-Inf, xend = ticks, yend = .77, 
               color = "grey70") +
  geom_hline(yintercept = 1) +
  xlab("forecast date") + ylab("Cumulative Geometric Mean") +
  coord_cartesian(#ylim = c(.76, 1), 
                  xlim = ymd(c("2020-06-01", "2021-01-01"))) +
  scale_x_date(date_breaks = "2 months", date_minor_breaks = "1 week",
               date_labels = "%b %Y") +
  scale_color_manual(values = fcast_colors, guide = guide_legend(nrow = 1)) +
  theme_bw() +
  theme(legend.position = "bottom", legend.title = element_blank(),
        panel.grid.minor.x = element_blank())
```

@@

<!-- Comparison to submitted forecasts -->

```{r grab-submitted-case-fcasts}
library(aws.s3)
Sys.setenv("AWS_DEFAULT_REGION" = "us-east-2")
s3bucket <- get_bucket("forecast-eval")
# ensure that forecasters have submitted a reasonable amount
n_keeper_weeks <- 6L
n_keeper_locs <- 50L
case_scores <- s3readRDS("score_cards_state_cases.rds", s3bucket) %>% 
  mutate(forecast_date = target_end_date - ahead * 7) %>% 
  # fix weirdnesses about submission dates, 
  # this is generous to the forecaster
  filter(forecast_date < "2021-01-01", ahead < 4) %>% 
  select(ahead, geo_value, forecaster, target_end_date, wis, forecast_date)

strawman <- case_scores %>% filter(forecaster == "COVIDhub-baseline")
case_scores <- left_join(
  case_scores, 
  strawman %>% 
    select(forecast_date, target_end_date, geo_value, wis) %>% 
    rename(strawman_wis = wis)
) %>% filter(forecaster != "COVIDhub-baseline")

# Subset to those forecasters that submitted enough 14-day ahead forecasts
n_submitted <- case_scores %>% 
  filter(ahead == 2) %>% 
  group_by(forecaster) %>% 
  summarise(nfcasts = n())
keepers <- n_submitted %>% 
  filter(nfcasts / n_keeper_locs > n_keeper_weeks - .0001, 
         forecaster != "COVIDhub-4_week_ensemble") %>% # same as CH-Ensemble 
  pull(forecaster)

case_scores <- case_scores %>% 
  filter(forecaster %in% keepers) %>%
  group_by(forecaster, ahead) %>%
  summarise(rel_wis = Mean(wis) / Mean(strawman_wis),
            geo_wis1 = GeoMean((wis + 1) / (strawman_wis + 1)),
            geo_wis = GeoMean(wis / strawman_wis))
```

```{r compare-to-hub-mean, fig.height = 8.5, fig.cap="This figure reproduces Figure 3 in the main paper but overlays scores for the forecasts submitted to the COVID-19 Forecast Hub. Grey lines correspond to the various teams that submitted during period our evaluation period. We have highlighted the COVIDhub-ensemble, which is the official forecast of the CDC."}
# Same as Fig 3 in the paper
df <- summarizer(fcasts_honest %>% filter(period != "jm") %>%
                   group_by(ahead, forecaster), "wis", NULL, 
                 "strawman_wis", Mean, c("aggr","scale"))
ggplot(df) +
  geom_line(aes(ahead, wis, color = forecaster)) + 
  geom_point(aes(ahead, wis, color = forecaster)) +
  theme_bw() +
  geom_hline(yintercept = 1, size = 1.5) +
  xlab("Days ahead") +
  ylab("Mean WIS (relative to baseline)") +
  scale_color_manual(values = c(fcast_colors, "CH-ensemble" = "lightblue"),
                     guide = guide_legend(nrow = 2)) +
  theme(legend.position = "bottom", legend.title = element_blank()) +
  geom_line(data = case_scores, 
            aes(ahead * 7, rel_wis, group = forecaster),
            color = "grey70") +
  geom_line(data = case_scores %>% filter(forecaster == "COVIDhub-ensemble"),
            aes(ahead * 7, rel_wis), color = "lightblue", size = 1.5) +
  scale_y_log10()
```

```{r compare-to-hub-geomean, fig.height = 8.5, fig.cap="This figure is similar to Figure \\ref{fig:fcast-adjusted}. In this case, we add 1 to both the forecaster WIS and the baseline WIS before scaling (to allow forecasters that achieve 0 error to appear), and we overlay scores for the forecasts submitted to the COVID-19 Forecast Hub. Grey lines correspond to the various teams that submitted during period our evaluation period. We have highlighted the COVIDhub-ensemble, which is the official forecast of the CDC."}
# Like supplement GeoMean figure, but adding 1
df2 <- fcasts_honest %>% 
  filter(period != "jm") %>%
  group_by(ahead, forecaster) %>%
  summarise(wis = GeoMean((wis + 1) / (strawman_wis + 1)))

ggplot(df2) +
  geom_line(aes(ahead, wis, color = forecaster)) + 
  geom_point(aes(ahead, wis, color = forecaster)) +
  theme_bw() +
  geom_hline(yintercept = 1, size = 1.5) +
  xlab("Days ahead") +
  ylab("Geometric mean of WIS (relative to baseline)") +
  scale_color_manual(values = c(fcast_colors, "CH-ensemble" = "lightblue"),
                     guide = guide_legend(nrow = 2)) +
  theme(legend.position = "bottom", legend.title = element_blank()) +
  geom_line(data = case_scores, 
            aes(ahead * 7, geo_wis1, group = forecaster),
            color = "grey70") +
  geom_line(data = case_scores %>% filter(forecaster == "COVIDhub-ensemble"),
            aes(ahead * 7, geo_wis1), color = "lightblue", size = 1.5) +
  scale_y_log10()
```

### 2021-09-30 forecast/paper/supplement.tex

\caption{\label{tab:dm-test}$P$-values for a Diebold-Mariano test for differences in forecast error. The test is for the null hypothesis of equal performance against the alternative that the indicator assisted model is better.}
\centering
\begin{tabular}[t]{lrrrrr}
\toprule
metric & CHNG-CLI & CHNG-COVID & CTIS-CLIIC & DV-CLI & Google-AA\\
\midrule
Geometric Mean Relative WIS & 0.141 & 0.076 & 0.000 & 0.059 & 0.008\\
Mean Relative WIS & 0.186 & 0.137 & 0.002 & 0.074 & 0.064\\
\bottomrule
\end{tabular}
\end{table}

@@

@@

@@

\caption{This figure shows the cumulative sum of WIS for each forecaster divided by the cumulative sum of WIS for the baseline model. The shaded background shows}\label{fig:cumulative-mean}
\end{figure}

@@

>>>>

\caption{\label{tab:dm-test}$P$-values for a one-sided Diebold-Mariano test for improvement in forecast error. The test is for the null hypothesis of equal performance against the alternative that the indicator assisted model is better.}
\centering
\begin{tabular}[t]{lrrrrr}
\toprule
metric & CHNG-CLI & CHNG-COVID & CTIS-CLIIC & DV-CLI & Google-AA\\
\midrule
Geometric Mean Relative WIS & 0.141 & 0.076 & 0.000 & 0.059 & 0.008\\
Mean Relative WIS & 0.186 & 0.137 & 0.002 & 0.074 & 0.064\\
\bottomrule
\end{tabular}
\end{table}

@@

{\centering \includegraphics[width=\textwidth]{fig/upswing-summary-remake-1}

\caption{REMAKE: Percent change in average WIS of the forecaster (AR or indicator assisted) relative to the baseline. All models perform poorly durning down periods, but the indicators help. During flat periods, the indicators improve slightly over the AR. During up periods, all forecasters do much better than the baseline, but only some do as well as AR.}\label{fig:upswing-summary-remake}
\end{figure}

@@

{\centering \includegraphics[width=\textwidth]{fig/hotspots-upswing-downswing-remake-1}

\caption{REMAKE: Classification and loglikelihood separated into periods of upswing, downswing, and flat cases. The indicator assisted models always have lower classification error relative to the null classifier, while the AR actually does worse in down and flat periods. In terms of loglikelihood, all forecasters have lower likelihood than the null classifier during up periods. In down and flat periods, the indicators generally improve over the AR, while the are worse during up periods.}\label{fig:hotspots-upswing-downswing-remake}
\end{figure}

@@

\caption{This figure shows the cumulative sum of WIS for each forecaster divided by the cumulative sum of WIS for the baseline model. The shaded background shows total U.S. cases as reported by JHU-CSSE for the 14-day ahead target. Hashes along the $x$-axis denote weeks.}\label{fig:cumulative-mean}
\end{figure}

{\centering \includegraphics[width=\textwidth]{fig/cumulative-geo-mean-1}

\caption{This figure shows the cumulative geometric mean of WIS for each forecaster divided by the WIS for the baseline model. The shaded background shows total U.S. cases as reported by JHU-CSSE for the 14-day ahead target. Hashes along the $x$-axis denote weeks.}\label{fig:cumulative-geo-mean}
\end{figure}

@@

{\centering \includegraphics[width=\textwidth]{fig/compare-to-hub-mean-1}

\caption{This figure reproduces Figure 3 in the main paper but overlays scores for the forecasts submitted to the COVID-19 Forecast Hub. Grey lines correspond to the various teams that submitted during period our evaluation period. We have highlighted the COVIDhub-ensemble, which is the official forecast of the CDC.}\label{fig:compare-to-hub-mean}
\end{figure}

{\centering \includegraphics[width=\textwidth]{fig/compare-to-hub-geomean-1}

\caption{This figure is similar to Figure \ref{fig:fcast-adjusted}. In this case, we add 1 to both the forecaster WIS and the baseline WIS before scaling (to allow forecasters that achieve 0 error to appear), and we overlay scores for the forecasts submitted to the COVID-19 Forecast Hub. Grey lines correspond to the various teams that submitted during period our evaluation period. We have highlighted the COVIDhub-ensemble, which is the official forecast of the CDC.}\label{fig:compare-to-hub-geomean}
\end{figure}
